Jane, John … Leslie? A Historical Method for Algorithmic Gender Detection

### 2014-09-08 article.Rmd
Overview of data; mention rOpenSci

To that end we have created the [Gender](https://github.com/ropensci/gender) package for R which contains the predictive algorithm, and an associated [genderdata](https://github.com/lmullen/gender-data-pkg) package which contains various historical datasets. This R implementation is based on an [earlier Python implementation](https://github.com/cblevins/Gender-ID-By-Time) by [Cameron Blevins](http://www.cameronblevins.org/) and [Bridget Baird](http://www.conncoll.edu/directories/emeritus-faculty/bridget-baird/).

@@

>>>>

To that end we have created the [Gender](https://github.com/ropensci/gender) package for R which contains the predictive algorithm, and an associated [genderdata](https://github.com/lmullen/gender-data-pkg) package which contains various historical datasets. This R implementation is based on an [earlier Python implementation](https://github.com/cblevins/Gender-ID-By-Time) by [Cameron Blevins](http://www.cameronblevins.org/) and [Bridget Baird](http://www.conncoll.edu/directories/emeritus-faculty/bridget-baird/). The Gender package is affiliated with [rOpenSci](http://ropensci.org/), an initiative that supports reproducible research and open data for scientists using R. The rOpenSci advisory board has provided code review and publicity for the project.

@@

 The Gender package currently includes two datasets which make it suitable for use for United States history since the first federal census in 1790.^[The authors of the package are both American historians, which explains why the initial release of the package focuses on that country. We have plans, however, to extend the underlying data to six other European and North American countries included in the [North Atlantic Population Project](https://www.nappdata.org/napp/) for the nineteenth century. We also welcome contributions of datasets for other regions and times from other scholars.] The first dataset contains names of applicants for Social Security and available from Data.gov. The second dataset contains names gathered in the decennial censuses and available from the IPUMS-USA (Integrated Public Use Microdata Series) service from the Minnesota Population Center at the University of Minnesota.
